The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-07-30 manuscript.Rmd
[fix #45] code effort through time by year instead of phylum

<!-- add sentence
We combined `r format(nrow(idigbio_records), big.mark=",")` museum records for marine invertebrates collected within the EEZ of the continental US representing `r length(unique(tolower(idigbio_records[["data.dwc:phylum"]])))` phyla and `r format(length(unique(idigbio_records$worms_valid_name)), big.mark=",")` species from iDigBio. Most samples were collected on the continental shelf (Fig. \@ref(fig:map-diversity-sampling)A). For the East coast, species richness is the highest in South Florida but it is relatively uniform along the coastline. For the West coast, the Pacific Northwest, the San Francisco Bay Area, and Southern California have the highest richness (Fig. \@ref(fig:map-diversity-sampling)B).

@@

```{r idigbio-through-time, fig.cap='Cumulative number of samples (A) and species (B) of marine invertebrates recorded through time based on iDigBio records. Relation between number of samples collected, and number of species recorded for the first time (C), each point represents numbers for a given year, dashed lines show the 1:1 and 1:100 ratios for number of species recorded for the first time and number of samples. (\\#fig:idigbio-through-time)'}
knitr::include_graphics("figures/idigbio_through_time.pdf")
```

>>>>

<!-- add sentence -->
We combined `r format(nrow(idigbio_records), big.mark=",")` museum records for marine invertebrates collected within the EEZ of the continental US representing `r length(unique(tolower(idigbio_records[["data.dwc:phylum"]])))` phyla and `r format(length(unique(idigbio_records$worms_valid_name)), big.mark=",")` species from iDigBio. Most samples were collected on the continental shelf (Fig. \@ref(fig:map-diversity-sampling)A). For the East coast, species richness is the highest in South Florida but it is relatively uniform along the coastline. For the West coast, the Pacific Northwest, the San Francisco Bay Area, and Southern California have the highest richness (Fig. \@ref(fig:map-diversity-sampling)B).

@@

```{r idigbio-through-time, fig.cap='Cumulative number of samples (A) and species (B) of marine invertebrates recorded through time based on iDigBio records. Relation between number of samples collected, and number of species recorded for the first time (C), each point represents numbers for a given year, dashed line show the 1:1 and dotted line the 1:100 ratios for number of species recorded for the first time to the number of samples. (\\#fig:idigbio-through-time)'}
knitr::include_graphics("figures/idigbio_through_time.pdf")
```
